Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma

### 2017-07-06 main.tex
Add table of wins for top winners.
Discussed on #4

@@

>>>>

Table~\ref{tbl:standard_wins_top_winners} shows the same information as
Table~\ref{tbl:standard_wins} but for the top 15 strategies who win the most
head to head matches.
% TODO Add more?

\begin{table}[!hbtp]
    \centering
        \input{./assets/standard_top_15_winners_wins_summary.tex}
        \caption{Standard Tournament: Number of wins per tournament
        of top 15 strategies (ranked by median wins over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
        \label{tbl:standard_wins_top_winners}
\end{table}

@@

Table~\ref{tbl:noisy_wins_top_winners} shows the same information as
Table~\ref{tbl:noisy_wins} but for the top 15 strategies who win the most
head to head matches.
% TODO Add more?

\begin{table}[!hbtp]
    \centering
        \input{./assets/noisy_top_15_winners_wins_summary.tex}
        \caption{Noisy (5\%) Tournament: Number of wins per tournament
        of top 15 strategies (ranked by median wins over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
        \label{tbl:noisy_wins_top_winners}
\end{table}
